Refinements for open automata

### 2022-03-07 2021-Refinement/paper/refinementarticle.tex
proof thm 3

there exist an indexed family of OTs originating from $s_3$: 

@@

Let $R$ be the refinement relation relating states of $A_1$ and $A_2$. 
Let us denote with $t^1$ and $t^2$  the elements of $A_1$ and $A_2$ respectively.
Consider any two states $s_{13} = \mpar{s_1,s^1_3}$ and $s_{23} = \mpar{s_2,s^2_3}$ ($s^1_3$ and $s^2_3$  are the same with renaming). We define a relation $R'$ relating states of $s_{13}$ and $s_{23}$ as follows:
\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in V_3}
\!\!\! v^1_3=v^2_3\wedge s^1_3 = s^2_3\]

@@

Considering that initial valuations $\sigma_{03}^1$ and $\sigma_{03}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left(\,\,\,\,{\displaystyle \bigwedge_\subbox{v_3\in vars(s_3)} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }$.

Because  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
\begin{align*}
& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3\\
\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
\implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
\end{align*}

@@

These two cases define (depending on how $t_{13}$ is built) the family $t_{23x}$ of OTs we are looking for.
Thus, for both cases we have to prove the following:
\begin{align*}		
		&\mpar{\forall x \in X, J'_{23x} \cap H' =
 J'_{13} \cap H'} \text{ and }\\
		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{align*}

@@

And suppose that  $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$ holds then we can deduce:
\begin{align*}
 V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}}\vdash &    \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3 \implies {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{2x}   \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}} \\  
\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in \Rightarrow   ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
\Rightarrow    V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}\\
\end{align*}
Finally, the composition gives $g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}$ and
$g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}$. \\
Furthermore, as $k \in H$ we have   
$\beta_{1k} = \beta_{2xk}$ then we  deduce:
$g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}$

@@

We can deduce for any transition $t_3$ in $A_3$ relying $s_3$ and $s^{\prime}_3$ we have:
\begin{multline*}
V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
\bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3  \wedge s^1_3 = s^2_3 \implies \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3)  \wedge s^{1\prime}_3 = s^{2\prime}_3 
 \end{multline*}	
Therefore, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
\implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\\
			 \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
\land \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3) \wedge s^{1\prime}_3 = s^{2\prime}_3
		\end{array}}   
\end{multline*}
And finally By hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
Thus, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
\wedge \bigwedge_\subbox{v_3\in \fvars{s_3}}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
		  \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
\wedge \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
		\end{array}}   
\end{multline*}	
Because of the domain of the substitutions of the relations, we get expected formula:\TODO{Point a verifier les substitutions!}
	\begin{multline*}
  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ R^{\prime}\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
			\nwedge g_{23x} \wedge R^{\prime}\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{multline*}

\item if $k \notin J'_1$:\\
The proof of this case follows the same steps as the previous case the only argument that changes is that  $g_{13} \Leftrightarrow g_1$ and
$g_{23x}  \Leftrightarrow g_{2x}$.
 \end{itemize}
\item The last formula we need to prove is the following: for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
\begin{multline*}
V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \\ \left(R^{\prime}\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \right)
\end{multline*}
Let's start  with the hypothesis of the theorem stating that $\wrel{A_1}{A_2}{H}$, thus we have for all  $\mpar{s_1, s_2} \in S_1 \times S_2$ 
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
\end{multline*}
We have a second hypothesis stating that the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking, which leads to:
\begin{multline*}
V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \left( \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \right)
\end{multline*}
We use the the first, we extend the valuation to cover the variables of  $t^2_3$ in $t_{23}$ using their value in $t_3$ and because $\fvars{t_{13}} \vdash \reach{A_{13}}\mpar{s_{13}}$, we get"
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}  \wedge \reach{A_{13}}\mpar{s_{13}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}   \wedge \reach{A_{13}}\mpar{s_{13}}\right)
\end{multline*}
By transitivity with the second hypothesis we obtain:
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
\end{multline*}
\TODO{verifier les contextes valuations} \qed
 \end{enumerate}

@@

% The proof requires  to rename the variables of one instance of the two $A_3$ automata to avoid clashes in variable names (this is required by the definition of refinement). In practice we will use superscripts ${}^1$ and ${}^2$ to distinguish elements of the two instances of $A_3$.
 \qed

>>>>

there exists an indexed family of OTs originating from $s_3$: 

@@

Let $R$ be the refinement relation relating states of $A_1$ and $A_2$. 
Let us denote with $t^1$ and $t^2$  the elements of $A_1$ and $A_2$ respectively.
Consider any two states $s_{13} = \mpar{s_1,s^1_3}$ and $s_{23} = \mpar{s_2,s^2_3}$ ($s^1_3$ and $s^2_3$  are the same with renaming). We define a relation $R'$ relating states of $s_{13}$ and $s_{23}$ as follows:
\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in V_3}
 v^1_3=v^2_3\wedge s^1_3 = s^2_3\]

@@

Considering that initial valuations $\sigma_{03}^1$ and $\sigma_{03}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }$.

Because  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
\begin{align*}
& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \land \mpar{\bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }\\
\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03}\uplus \sigma_{013} }\\
\implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
\end{align*}

@@

These two cases define (depending on how $t_{13}$ is built) the family $t_{23x}$ of OTs we are looking for.
Thus, for both cases we have to prove the following:
\begin{align*}		
		&\mpar{\forall x \in X, J'_{23x} \cap H' =
 J'_{13} \cap H'} \text{ and }\\
		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ & R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{align*}

@@

And suppose that  $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$ holds then we can deduce:
\begin{align*}
 V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}}\vdash &    \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3 \implies {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{2x}   \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}} \\  
\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in \Rightarrow   ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
\Rightarrow    V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}
\end{align*}
Finally, the composition gives $g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}$ and
$g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}$. \\
Furthermore, as $k \in H$ we have   
$\beta_{1k} = \beta_{2xk}$ then we  deduce:
$g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}$

@@

We can deduce for any transition $t_3$ in $A_3$ relying $s_3$ and $s^{\prime}_3$ we have:
\begin{multline*}
V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
\bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3  \wedge s^1_3 = s^2_3 \implies \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3)  \wedge s^{1\prime}_3 = s^{2\prime}_3 
 \end{multline*}	
Therefore, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
\implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land\\
			 \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
 \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3) \wedge s^{1\prime}_3 = s^{2\prime}_3
		\end{array}}   
\end{multline*}
And finally By hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
Thus, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
		  \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
\wedge \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
		\end{array}}   
\end{multline*}	
Because of the independence of the substitution domains, we get the expected formula:
	\begin{multline*}
  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ R^{\prime}\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
			\nwedge g_{23x} \wedge R^{\prime}\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{multline*}

\item if $k \notin J'_1$:\\
The proof of this case follows the same steps as the previous case the only argument that changes is that  $g_{13} \Leftrightarrow g_1$ and
$g_{23x}  \Leftrightarrow g_{2x}$.
 \end{itemize}
\item The last formula we need to prove is the following: for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
\begin{multline*}
V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \\ \left(R^{\prime}\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \right)
\end{multline*}
Let's start  with the hypothesis of the theorem stating that $\wrel{A_1}{A_2}{H}$, thus we have for all  $\mpar{s_1, s_2} \in S_1 \times S_2$ 
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
\end{multline*}
We have a second hypothesis stating that the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking, which leads to:
\begin{multline*}
V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \left( \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \right)
\end{multline*}
We use the the first, we extend the valuation to cover the variables of  $t^2_3$ in $t_{23}$ using their value in $t_3$ and because $\fvars{t_{13}} \vdash \reach{A_{13}}\mpar{s_{13}}$, we get"
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}  \wedge \reach{A_{13}}\mpar{s_{13}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}   \wedge \reach{A_{13}}\mpar{s_{13}}\right)
\end{multline*}
By transitivity with the second hypothesis we obtain:
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
\end{multline*}
That implies:
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(\underbrace{R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3}_{R^{\prime}(s_{13},s_{23})}  \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
\end{multline*}
which gives us what we needed to demonstrate. \qed
 \end{enumerate}

@@

% The proof requires  to rename the variables of one instance of the two $A_3$ automata to avoid clashes in variable names (this is required by the definition of refinement). In practice we will use superscripts ${}^1$ and ${}^2$ to distinguish elements of the two instances of $A_3$.

Let $R$ be the refinement relation relating states of $A_2$ and $A_3$. 
Let us denote with $t^2$ and $t^3$  the elements of $A_2$ and $A_3$ respectively.
Consider any two states $s_{12} = \mpar{s_1,s^1_2}$ and $s_{13} = \mpar{s^2_1,s_3}$ ($s^1_1$ and $s^2_1$  are the same with renaming). We define a relation $R'$ relating states of $s_{12}$ and $s_{13}$ as follows:
\[ R' \mpar{s_{12}, s_{13}} = R\mpar{s_{2}, s_{2}} \wedge \reach{A_{12}}\mpar{s_{12}} \wedge \bigwedge_\subbox{v_1\in V_1}
 v^1_1=v^2_1\wedge s^1_1 = s^2_1\]
Let us denote $H'=H\cup J_1 \setminus\{k\}$.
We want to prove that $\mpar{R', H'}$  is a hole-tracking simulation of $A_{12}$ and $A_{13}$. As for the previous proof we deal with cases:
\begin{enumerate}
\item We have to prove that it holds for the initial configurations:
\[\sigma_{012} \uplus \sigma_{013} \vdash R'\mpar{s_{012}, s_{013}}\]
with $\sigma_{012} = \sigma_{01}^1 \uplus \sigma_{02}$, $\sigma_{013} = \sigma_{01}^2 \uplus \sigma_{03}$, $s_{012}=(s_{01}^1,s_{02})$, and $s_{013}=(s_{01}^2,s_{03})$.\\
By using the fact that $R$ relates initial configurations of  $A_2$ and $A_3$, we have  the following statement:
$\mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}}$,  and relying on the  fact that initial states are reachable $\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}$ we have 
\[ \mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}} \wedge 
\mpar{\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}}\]
Because initial valuations $\sigma_{01}^1$ and $\sigma_{01}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1}\right)\psubst{\sigma_{01}^1 \uplus \sigma_{01}^2 }$.

Furthermore, because  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
\begin{align*}
& \mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}} \wedge 
\mpar{\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}}\\
\implies & R\mpar{s_{02}, s_{03}}\psubst{ \sigma_{02} \uplus \sigma_{03}} \wedge \reach{A_{12}}\mpar{s_{012}} \psubst{\sigma_{012}} \land \mpar{ {\displaystyle \bigwedge_\subbox{v_1\in V_1}\,\, v^1_1=v^2_1\wedge s^1_1 = s^2_1}}\psubst{\sigma_{01}^1 \uplus \sigma_{01}^2 }\\
\implies & \mpar{R\mpar{s_{02}, s_{03}} \wedge \reach{A_{12}}\mpar{s_{012}}  \wedge \bigwedge_\subbox{v_1\in V_1}  v^1_1=v^2_1\wedge s^1_1 = s^2_1} \psubst{ \sigma_{02} \uplus \sigma_{03} \uplus \sigma^1_{01}\uplus \sigma^2_{01} \uplus \sigma_{012}}\\
\implies & \sigma_{012} \uplus \sigma_{013} \vdash R'\mpar{s_{012}, s_{013}}
\end{align*}

\item Second, we need to prove for any OT $t_{12}$ in $T_{12}$ originating from $s_{12}$

\begin{align*}
		&  \OTx{12}{}{12}{12} \in \fOT{s_{12}}
\end{align*}		
there exists an indexed family $t_{13x}$ of OTs originating from $s_{13}$ that simulates it: 
\begin{align*}
		&  \mpar{\OTx{13}{x}{13x}{13x} \in \fOT{s_{13}}}^{x \in X}
\end{align*}	
such that  $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and\\

\begin{align*}		
V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
		\end{array}} 
	\end{align*}
By definition of composition and open automata refinement we have: 
\begin{align*}
&V_{12}= V^1_1\uplus V_3 \text{ and }
V_{13}= V^2_1\uplus V_3\\
& H'=H_{23}\uplus J_1 \setminus \{k\} \subseteq J_1\uplus \mpar{J_2 \cap J_3} \setminus \{k\} = \mpar{J_1\uplus J_2 \setminus \{k\} } \cap \mpar{J_1\uplus J_3 \setminus \{k\}} = J_{13} \cap J_{13} \\
\end{align*}
~\qed
\end{enumerate}
